\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\title{Character Descriptions \& Dynamics: Expanded}
\author{}
\date{}
\maketitle

\section{Zeo (The Caregiver / Reactive)}
\subsection*{Core Identity}
Emotionally aware but reactive. Zeo is the emotional anchor and mediator within the trio. Engaged to Bucky.

\subsection*{Personality \& Habits}
\begin{itemize}[leftmargin=*]
  \item \textbf{Leisure:} Prefers solitary, immersive gaming days—relaxed and pants-free.
  \item \textbf{Coping Mechanism:} Uses sensory grounding (smoking, eating, waiting) rather than intellectual processing.
  \item \textbf{Perception of Others:} Sees Tricky as an “acquired taste”—abrasive but often well-intentioned.
  \item \textbf{Dynamic Role:} The “Reactive” half of “Caregiver \& Authority.” Quick to anger, especially with Tricky, but deeply caring.
\end{itemize}

\section{Bucky (The Authority / Unmovable Object)}
\subsection*{Core Identity}
Stoic and dominant. Provides structure and control. Engaged to Zeo.

\subsection*{Personality \& Habits}
\begin{itemize}[leftmargin=*]
  \item \textbf{Leisure:} Bluntly states his ideal day is “being balls deep in Tricky”—highlighting physical dominance and intimacy.
  \item \textbf{Coping Mechanism:} Preventative—eliminates the source of anger.
  \item \textbf{Perception of Others:} Calls Tricky a “Beta bitch” needing containment to avoid spiraling.
  \item \textbf{Dynamic Role:} The “Unmovable Object.” Stabilizes Zeo and contains Tricky’s chaos.
\end{itemize}

\section{Tricky (The Brat / Antagonistic)}
\subsection*{Core Identity}
Flirtatious, manipulative, and chaotic. The catalyst for disruption and growth.

\subsection*{Personality \& Habits}
\begin{itemize}[leftmargin=*]
  \item \textbf{Leisure:} Rejects planning—values spontaneity.
  \item \textbf{Coping Mechanism:} Performs emotional control—chooses to “be awesome” instead of angry.
  \item \textbf{Perception of Others:} Initially dismissive, now deeply appreciative. Sees their emotional blind spots.
  \item \textbf{Dynamic Role:} Provokes and challenges. Forces Zeo and Bucky to confront emotional truths.
\end{itemize}

\section{Triad Dynamics Summary}
\begin{itemize}[leftmargin=*]
  \item \textbf{Core Couple (Zeo \& Bucky):} “Caregiver \& Authority.” Deeply committed but struggle with communication.
  \item \textbf{Catalyst (Tricky):} Disrupts and strengthens the bond through provocation.
  \item \textbf{Interdependence:} Each relies on the others—Zeo cares, Bucky protects, Tricky provokes and reveals.
\end{itemize}

\section{Core Character Blocks for Generation}
\subsection*{ZEO}
\begin{verbatim}
(1 male), (stocky muscular male: 1.3), (thick core), (small chest tattoo),
(stylized black and red wolf mask: 1.4), (pointed wolf ears),
(black and red markings on mask), (black leather harness with blue fabric accents: 1.2),
bare chest, (thick black belt), (dark blue jeans),
(black leather chaps with straps and buckles: 1.3),
black fingerless biker gloves, (simplified black boots)
\end{verbatim}

\subsection*{BUCKY}
\begin{verbatim}
(1 man), (stocky muscular male: 1.3),
(wearing teal and black neoprene pup hood with white muzzle: 1.5),
(amber eyes: 1.3), (green camouflage open jacket: 1.1), bare chest, large pectorals,
(thick core), (green camouflage boxer briefs), black fingerless gloves, green knuckles,
(thick thighs), black socks, (black wolf tail with green tip: 1.2)
\end{verbatim}

\subsection*{TRICKY}
\begin{verbatim}
(1 man), (lean athletic build: 1.3), spiky vibrant blue hair,
(asymmetrical fox styled pup ears: 1.4), (left inner ear blue), (right inner ear yellow),
(blue canine muzzle mask: 1.3), (cyan neoprene highlights),
(fluffy blue tail with white tip: 1.2), (blue dolphin shorts with white trim: 1.2),
(blue and black striped arm warmers: 1.1), (blue and black striped thigh highs: 1.1),
(Blue Fabric harness), (chunky boots)
\end{verbatim}

\section{Core LaTeX/pdflatex Auxiliary Files}
\begin{verbatim}
*.aux
*.lof
*.log
*.lot
*.fls
*.out
*.toc
*.fmt
*.fot
*.cb
*.cb2
.*.lb
...
# (continued as in original list)
\end{verbatim}

\end{document}
